\textbf{Response Letter}

### 2018-12-01 doc/aij18/major-revision/letter.tex
updates in response letter

\usepackage[framemethod=tikz]{mdframed}

\mathchardef\mh="2D
\newcommand{\pre}{\mathsf{pre}}       % precondition
\newcommand{\eff}{\mathsf{eff}}       % effect
\newcommand{\cond}{\mathsf{cond}}     % conditional effect
\newcommand{\add}{\mathsf{add}}       % add effect
\newcommand{\del}{\mathsf{del}}       % delete effect
\newcommand{\PE}{\mathrm{PE}}         % precondition
\newcommand{\PSPACE}{\mathrm{PSPACE}} % PSPACE
\newcommand{\strips}{\textsc{Strips}} % Strips

\begin{document}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
I suggest to describe the overall concept of the learning approach first (see above for my hopefully correct summary) and to give the technical details later, rather than describing the technical details of compilation only without providing the overall picture. Going top down would make reading much easier. The second reason for revision is the comparison to ARMS. I suggest to compare with LOUGA that is better than ARMS in all aspects (runtime and quality of obtained models) so ARMS is no more state-of-the-art.
\end{mdframed}

>>>>

\usepackage[framemethod=tikz]{mdframed}
\usepackage{xspace}

\mathchardef\mh="2D
\newcommand{\pre}{\mathsf{pre}}       % precondition
\newcommand{\eff}{\mathsf{eff}}       % effect
\newcommand{\cond}{\mathsf{cond}}     % conditional effect
\newcommand{\add}{\mathsf{add}}       % add effect
\newcommand{\del}{\mathsf{del}}       % delete effect
\newcommand{\PE}{\mathrm{PE}}         % precondition
\newcommand{\PSPACE}{\mathrm{PSPACE}} % PSPACE
\newcommand{\strips}{\textsc{Strips}} % Strips
\newcommand{\FAMA}{{\small {\sffamily FAMA}}\xspace}

\title{\textbf{Response Letter}}
\begin{document}
\maketitle

Firstly, we would like to thank the three reviewers for their insightful comments and recommendations. We truly believe the observations pointed by the three reviewers have been very helpful to make the paper more readable.

This response letter is structured as follows. The next section summarizes the most relevant modifications addressed in the paper. Subsequent sections are devoted to thoroughly reply all the reviewers' concerns.

\subsection*{Main modifications addressed in the paper}

We identified four main points to be addressed as per the reviewers' comments and observations. In this section, we provide details of these four main modifications, and we will point at them when replying to each of the reviewers' comments in the remainder sections.

\begin{itemize}
\item \textbf{Introduction}. We performed a profound revision of the Introduction in order to make it more self-explanatory. First, we carefully revised all of the comments pointed by reviewer \#2. Additionally, as indicated by reviewer \#1, we provide at the end of the section the overall picture of our approach. Our modification is intended to adequately position our contribution within the concerned research field, and to provide a global picture of the \FAMA approach that explains our pursued objective.

\item \textbf{Problem definition and complexity}. As indicated by reviewer \#2, and also supported by reviewers \#1 and \#3, the problem definition is not clearly introduced,. We believe this is the reason that our claims about the complexity of the learning task were not fully comprehensible. We acknowledge this lack of problem definition, and we introduce a subsection 3.1 to clearly define upfront the basic and essence of the learning task we are aimed to solve.

\item \textbf{Compilation scheme}. Reviewers \#1 and \#3 show several concerns about the understanding of section 4.4., the compilation approach. We acknowledge their concerns and we have thus introduced an introductory explanatory subsection that explains .......... before going into the technical details. We hope this new subsection will help the reader to have first a broad view of the compilation scheme before diving into the technicalities.

\end{itemize}

@@

\begin{mdframed}[hidealllines=true,backgroundcolor=gray!20]
I suggest to describe the overall concept of the learning approach first (see above for my hopefully correct summary) and to give the technical details later, rather than describing the technical details of compilation only without providing the overall picture. Going top down would make reading much easier. The second reason for revision is the comparison to ARMS.
\end{mdframed}

We agree with the reviewer that we should provide ....

\begin{mdframed} [hidealllines=true,backgroundcolor=gray!20]
I suggest to compare with LOUGA that is better than ARMS in all aspects (runtime and quality of obtained models) so ARMS is no more state-of-the-art.
\end{mdframed}

As per the reviewer's recommendation, we requested the code of LOUGA to the first author of the publication entitled \emph{LOUGA: learning planning operators using genetic algorithms}, which was published in the Pacific Rim Knowledge Acquisition Workshop. The author of LOUGA promptly provided us with the code, so we would first like to thank him for his gentle response. However, the issue we faced with LOUGA is that we were not able to automate the processing and output of the results. LOUGA throws results in a graphical interface, which makes it hard to easily retrieve the data to be subsequently processed. Since the input of our automated process for extracting the experimental results are plain text files, we could not adapt the graphical output of LOUGA to our required input. Nevertheless, we did test a couple of ....
